An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-15 paper.tex

\section*{Conclusion}
%
We have presented the details of what we believe to be a rich and elaborate
data set of motion and ground reaction loads humans exhibit during both normal
walking and when recovering from longitudinal perturbations. The data provides
a very large sample of gait cycles from both unperturbed and perturbed walking
at three different nominal speeds. The raw data is provided for reuse with
complete meta data. In addition to the data, we provide software that can
process the data for both cleaning purposes and to produce typical sagittal
plane gait variables of interest. The variation of these gait variables and
statistics are provided to give a high level picture of the character of the
data. Among other uses, we believe the dataset is ideally suited for control
identification purposes. Many researchers are working on mathematical models
for control in gait and this dataset provides both a way to validate these
models and a source for generating them.

>>>>

\section*{Conclusion}
%
We have presented a rich and elaborate data set of motion and ground reaction
loads from human subjects during both normal walking and when recovering from
longitudinal perturbations. The raw data is provided for reuse with complete
meta data. In addition to the data, we provide software that can process the
data for both cleaning purposes and to produce typical sagittal plane gait
variables of interest. Among other uses, we believe the dataset is ideally
suited for control identification purposes. Many researchers are working on
mathematical models for control in gait and this dataset provides both a way to
validate these models and a source for generating them.
